Mapping plant-pollinator interactions across Europe

### 2023-12-15 Manuscript/Figure1.qmd
Minor data edits

#Try to plot both together (same plot)
map = ggplot(countries) +
geom_sf(fill="floralwhite",color = "black", 
        alpha = 1,linewidth=0.1) + 
geom_star(data = all_data, alpha=1,aes(x= Longitude, y=Latitude,
           size=Counts, starshape = Group, color= Group))+  
coord_sf(crs = st_crs(3035), default_crs = st_crs(4326),
         xlim = c(-14, 39), ylim = c(37, 70))+
theme(panel.grid.major = element_blank(), 
      legend.position = ("top"),
      legend.box = "vertical",
      legend.background = element_blank(),
      legend.box.background = element_blank(),
      legend.key = element_blank(), 
      legend.title = element_text(face =                "bold",  size = 6),
      legend.box.spacing = unit(0, "pt"),
      axis.text = element_text(size=6,                  face="bold"),
      axis.title = element_text(face="bold", size = 8),
         legend.text = element_text(face = "bold",
         size = 6), legend.direction="horizontal",
         legend.spacing.y = unit(-0.4, "cm"),
      legend.title.align=0.5) +
theme(panel.background = element_rect(fill = "aliceblue"),
        panel.border = element_rect(colour = "black",
        fill=NA, size=1)) + 
 scale_size_continuous(range = c(0, 4))+
scale_color_manual(values=c("#009E73", "#D55E00"),
         guide="none") +
scale_starshape_manual(name = "Taxonomic\ngroup",             values = c(15, 7),
             guide=guide_legend(
             override.aes=list(
                 size=2,
                 color=c("Plant"="#009E73", "Pollinator"= "#D55E00")))) +
  ylab("Latitude") +
xlab("Longitude") +
scale_x_continuous(breaks = seq(0, 20, by = 10)) +
scale_y_continuous(breaks = seq(40, 60, by = 10)) +
guides(color = "none", size=guide_legend(nrow=1,override.aes = list(starshape =c(15,7, 15)))) + 
ggtitle("(a)") +
theme(plot.title = element_text(vjust = -18, hjust=0.12, size=10))

@@

#Seelect quantile 50% from the total number of species
spp_number = poll_spread %>%  
select(Pollinator_accepted_name) %>% 
n_distinct()
df = seq(1, spp_number)
quantile_50 = quantile(df, 0.5)
#Plot
p1 = ggplot(poll_spread, 
aes(reorder(Pollinator_accepted_name,-Percent_total), Percent_total)) +
geom_bar(stat = "identity", 
           color = "#D55E00",
           lwd = 0.015, fill = "#D55E00") +
ylab("Shared pollinators (%)") +
theme_minimal()+
theme(axis.text.x = element_blank(),
  axis.ticks.x=element_blank(),
  axis.ticks.y = element_line(size = 0.2),
  plot.title = element_text(size = 8, face = "bold"), 
  axis.text.y = element_text(size=6),
  panel.grid.major.x = element_blank(),
  panel.grid.minor.y = element_blank(),
  panel.grid.major.y = element_line(size=0.2, linetype =           2)) +
xlab(NULL) +
ylab(NULL) + 
ggtitle("Pollinators")+
geom_vline(xintercept = quantile_50, linetype="dashed", 
color = "black", size=0.25) + 
annotate(geom="text", x=1280, y=0.83, label="50th percentile", color="black", size = 1.5) +
scale_y_continuous(breaks = seq(0, 0.75, by= 0.25), expand = c(0, 0)) + 
annotate(geom="text", x=-500, y=1.71, label="(b)",color="black", size = 3.5) +
coord_cartesian(xlim=c(0, nlevels(factor(poll_spread$Pollinator_accepted_name))),ylim=c(0, max(poll_spread$Percent_total)), clip="off")

@@

#Seelect quantile 50% from the total number of species
spp_number = plant_spread %>%  
select(Plant_accepted_name) %>% 
n_distinct()
df = seq(1, spp_number)
quantile_50 = quantile(df, 0.5)
#Plot
p2 = ggplot(plant_spread, 
aes(reorder(Plant_accepted_name,-Percent_total), Percent_total, fill = Plant_accepted_name)) +
geom_bar(stat = "identity", 
           color = "#009E73",
           lwd = 0.015, fill = "#009E73") +
ylab("Shared plants (%)") +
theme_minimal()+
theme(axis.text.x = element_blank(),
         axis.ticks.x=element_blank(),
         axis.ticks.y = element_line(size = 0.2),
         axis.title.x = element_text(face = "bold", size = 8),            plot.title = element_text(size = 8, face = "bold"),
         axis.text.y = element_text(size=6),
         panel.grid.major.x = element_blank(),
         panel.grid.minor.y = element_blank(),
         panel.grid.major.y = element_line(size=0.2, linetype =           2)) +
xlab("Species") +
ylab(NULL) + 
ggtitle("Plants") + 
geom_vline(xintercept = quantile_50, linetype="dashed", 
          color = "black", size=0.25) + 
annotate(geom="text", x=830, y=0.7, label="50th percentile",color="black", size = 1.5) +
scale_y_continuous(breaks = seq(0, 0.6, by= 0.2), expand = c(0, 0), labels = label_number(accuracy = 0.01)) +
coord_cartesian(xlim=c(0, nlevels(factor(plant_spread$Plant_accepted_name))),ylim=c(0, max(plant_spread$Percent_total)), clip="off")

#Prepare panel with plots
plot2 =  wrap_elements(p1 / p2) +  labs(tag ="Percentage of studies              \n sharing a species              ") + 
theme(plot.tag = element_text(size = 7, angle = 90, face = "bold", vjust = -3.5), plot.tag.position = "left")
#Plot everything
map + plot_spacer() + plot2 + plot_layout(widths = c(2.1, -0.65, 1))

>>>>

#Try to plot both together (same plot)
map = ggplot(countries) +
geom_sf(fill="floralwhite",color = "black", 
        alpha = 1,linewidth=0.1) + 
geom_star(data = all_data, alpha=1,aes(x= Longitude, y=Latitude,
           size=Counts, starshape = Group, color= Group))+  
coord_sf(crs = st_crs(3035), default_crs = st_crs(4326),
         xlim = c(-14, 39), ylim = c(37, 70))+
theme(panel.grid.major = element_blank(), 
      legend.position = ("top"),
      legend.box = "vertical",
      legend.background = element_blank(),
      legend.box.background = element_blank(),
      legend.key = element_blank(), 
      legend.title = element_text(face ="bold",  size = 6),
      legend.box.spacing = unit(0.2, "cm"),
      legend.margin=margin(0,0,0,0),
        legend.box.margin=margin(-10,-10,-10,-10),
      axis.text = element_text(size=6,                  face="bold"),
      axis.title = element_text(face="bold", size = 8),
         legend.text = element_text(size = 6),                           legend.direction="horizontal",
         legend.spacing.y = unit(-0.3, "cm"),
      legend.title.align=0.5) +
theme(panel.background = element_rect(fill = "aliceblue"),
        panel.border = element_rect(colour = "black",
        fill=NA, size=1)) + 
 scale_size_continuous(name= "Species counts",range = c(0, 3.75))+
scale_color_manual(values=c("#009E73", "#D55E00"),
         guide="none") +
scale_starshape_manual(name = "Taxonomic group",             values = c(15, 7),
             guide=guide_legend(reverse=TRUE,
             override.aes=list(
                 size=2,
                 color=c("Pollinator"= "#D55E00","Plant"="#009E73")))) +
  ylab("Latitude") +
xlab("Longitude") +
scale_x_continuous(breaks = seq(0, 20, by = 10)) +
scale_y_continuous(breaks = seq(40, 60, by = 10)) +
guides(color = "none", size=guide_legend(nrow=1,override.aes = list(starshape =c(15,15, 15), size=c(0.8,1.8,2.8)))) + 
ggtitle("(a)") +
theme(plot.title = element_text(vjust = -12, hjust=0.1, size=10))

@@

#Seelect quantile 50% from the total number of species
spp_number = poll_spread %>%  
select(Pollinator_accepted_name) %>% 
n_distinct()
df = seq(1, spp_number)
quantile_50 = quantile(df, 0.5)

#Obtain most common pollinator for plotting
most_common_poll = poll_spread %>% filter(n_studies_shared == max(n_studies_shared)) %>%
select(Pollinator_accepted_name) %>% pull()

#Plot
p1 = ggplot(poll_spread, 
aes(reorder(Pollinator_accepted_name,-Percent_total), Percent_total)) +
geom_bar(stat = "identity", 
           color = "#D55E00",
           lwd = 0.015, fill = "#D55E00") +
ylab("Shared pollinators (%)") +
theme_minimal()+
theme(axis.text.x = element_blank(),
  axis.ticks.x=element_blank(),
  axis.ticks.y = element_line(size = 0.2),
  plot.title = element_text(size = 8, face = "bold"), 
  axis.text.y = element_text(size=6),
  panel.grid.major.x = element_blank(),
  panel.grid.minor.y = element_blank(),
  panel.grid.major.y = element_line(size=0.2, linetype =           2)) +
xlab(NULL) +
ylab(NULL) + 
ggtitle("Pollinators")+
geom_vline(xintercept = quantile_50, linetype="dashed", 
color = "black", size=0.25) + 
annotate(geom="text", x=1285, y=0.83, label="50th percentile",          color="black", size = 1.5) +
annotate(geom="text", x=20, y=0.88, label=most_common_poll[1],         color="black",  fontface = 'italic', size = 1.5)+
scale_y_continuous(breaks = seq(0, 0.75, by= 0.25), expand = c(0, 0)) + 
annotate(geom="text", x=-500, y=1.15, label="(b)",color="black", size = 3.5) +
coord_cartesian(xlim=c(0, nlevels(factor(poll_spread$Pollinator_accepted_name))),ylim=c(0, max(poll_spread$Percent_total)), clip="off")

@@

#Seelect quantile 50% from the total number of species
spp_number = plant_spread %>%  
select(Plant_accepted_name) %>% 
n_distinct()
df = seq(1, spp_number)
quantile_50 = quantile(df, 0.5)

#Obtain most common plant for plotting
most_common_plant = plant_spread %>% filter(n_studies_shared == max(n_studies_shared)) %>%
select(Plant_accepted_name) %>% pull()

#Plot
p2 = ggplot(plant_spread, 
aes(reorder(Plant_accepted_name,-Percent_total), Percent_total, fill = Plant_accepted_name)) +
geom_bar(stat = "identity", 
           color = "#009E73",
           lwd = 0.015, fill = "#009E73") +
ylab("Shared plants (%)") +
theme_minimal()+
theme(axis.text.x = element_blank(),
         axis.ticks.x=element_blank(),
         axis.ticks.y = element_line(size = 0.2),
         axis.title.x = element_text(face = "bold", size = 8),            plot.title = element_text(size = 8, face = "bold"),
         axis.text.y = element_text(size=6),
         panel.grid.major.x = element_blank(),
         panel.grid.minor.y = element_blank(),
         panel.grid.major.y = element_line(size=0.2, linetype =           2)) +
xlab("Species") +
ylab(NULL) + 
ggtitle("Plants") + 
geom_vline(xintercept = quantile_50, linetype="dashed", 
          color = "black", size=0.25) + 
annotate(geom="text", x=835, y=0.7, label="50th percentile",color="black", size = 1.5) + 
annotate(geom="text", x=20, y=0.75, label=most_common_plant[1]
      ,color="black",  fontface = 'italic', size = 1.5)+
annotate(geom="text", x=20, y=-0.08, label="Common spp."
      ,color="black",  size = 1.5) +
annotate(geom="text", x=1200, y=-0.08, label="\'Rare\' spp."
      ,color="black",  size = 1.5) + 
scale_y_continuous(breaks = seq(0, 0.6, by= 0.2), expand = c(0, 0), labels = label_number(accuracy = 0.01)) +
coord_cartesian(xlim=c(0, nlevels(factor(plant_spread$Plant_accepted_name))),ylim=c(0, max(plant_spread$Percent_total)), clip="off")

#Prepare panel with plots
plot2 =  wrap_elements(p1 / p2) +  labs(tag ="Occurrence across studies (%)") + 
theme(plot.tag = element_text(size = 7, angle = 90, face = "bold", vjust = -3.5), plot.tag.position = "left")
#Plot everything
map + plot_spacer() + plot2 + plot_layout(widths = c(2.1, -0.45, 1))

### 2023-12-15 Manuscript/Ms.qmd
Minor data edits

---
title: "Mapping plant-pollinator interactions across Europe"
format: pdf
editor: visual
---

```{r Load libraries, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE}
library(dplyr)
library(ggplot2)
library(giscoR)
library(sf)
```

@@

Pollinators play a crucial role in maintaining Earth's terrestrial biodiversity and human food production by mediating sexual reproduction for most flowering plants. However, their diversity and role as pollinators are increasingly compromised by rapid human-induced environmental changes. One of the major challenges for pollinator conservation, is the lack of robust generalisable data across space and time. Here, we present a dataset of plant-pollinator interactions at European level that consists of `r study_number` studies that cover `r country_number` countries and comprised over a million of interactions between plants and pollinators.

and explore the first European metaweb of plant-pollinator interactions. This is a continent-level metaweb that comprised of xxx plants xxx pollinators and xxxx interactions which covers xxxx different countries. We show that plant and pollinator species are xxxxx and have xxxxxxx. For instance, we cover xxx% of European bee species and xxx% of flowering plants that rely on pollinators.

@@

@@

```{r echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, out.width="100%"}
#Prepare coordinates
for_plotting = data %>% 
select(Study_id, Latitude, Longitude) %>% 
distinct()
#Get countries and transfrom coordinates
countries <- gisco_get_countries(
resolution = 20) %>%
st_transform(3035) %>% 
sf::st_as_sf(crs = 4326)

#Number of plant and poll species per network
#-----------------------#
#Pollinators------
#-----------------------#
#Check unique number of pollinator species
PollNumber_by_ID = data %>% 
select(Pollinator_rank, Pollinator_accepted_name, Study_id) %>% 
filter(Pollinator_rank == "SPECIES") %>% 
select(Pollinator_accepted_name, Study_id) %>% 
group_by(Study_id) %>% 
summarise(Pollinator_counts = n_distinct(Pollinator_accepted_name))
#Merge now with spp counts by network dataset
poll_data = left_join(PollNumber_by_ID, for_plotting, by = "Study_id")
#Create duplicate cord columns to operate on them
poll_data$coords <- data.frame(
Longitude = poll_data$Longitude, Latitude = poll_data$Latitude)
#Set coordinates
poll_data$coords_sf = st_as_sf(poll_data$coords, 
  coords = c("Longitude", "Latitude"), crs = 4326)
#Plot map of Europe
#Very noisy with many coordinates per point,
#Let's select a unique coordinate by study
poll_data1 =  poll_data %>% 
distinct(Study_id, .keep_all = TRUE)
#-----------------------#
#Plants-----
#-----------------------#
#Check unique number of plant species
PlantNumber_by_ID = data %>% 
select(Plant_rank, Plant_accepted_name, Study_id) %>% 
filter(Plant_rank == "SPECIES") %>% 
select(Plant_accepted_name, Study_id) %>% 
group_by(Study_id) %>% 
summarise(Plant_counts = n_distinct(Plant_accepted_name))
#Merge now with spp counts by network dataset
plant_data = left_join(PlantNumber_by_ID, for_plotting, by = "Study_id")
#Create duplicate cord columns to operate on them
plant_data$coords <- data.frame(
Longitude = plant_data$Longitude, Latitude = plant_data$Latitude)
#Set coordinates
plant_data$coords_sf = st_as_sf(plant_data$coords, 
  coords = c("Longitude", "Latitude"), crs = 4326)
#Plot map of Europe
#Very noisy with many coordinates per point,
#Let's select a unique coordinate by study
plant_data1 =  plant_data %>% 
distinct(Study_id, .keep_all = TRUE)
#Add vars
plant_data1$Group = "Plant"
poll_data1$Group = "Pollinator"
#Rename cols
plant_data2 = plant_data1 %>% 
rename(Counts = Plant_counts)
poll_data2 = poll_data1 %>% 
rename(Counts = Pollinator_counts)
#Bind rows
all_data = bind_rows(plant_data2, poll_data2)

#Try to plot both together (same plot)
ggplot(countries) +
geom_sf(fill="gray80",color = "black", 
        alpha = 1,linewidth=0.1) + 
geom_point(data = all_data, alpha=1,shape=21,
           aes(x= Longitude, y=Latitude,
           size=Counts, group=Group, colour = Group))+  
coord_sf(crs = st_crs(3035), default_crs = st_crs(4326),
         xlim = c(-14, 39), ylim = c(37, 70))+
theme(panel.grid.major = element_blank(), 
      legend.position = ("right"),
         legend.background = element_blank(),
         legend.box.background = element_blank(),
         legend.key = element_blank(), 
         legend.title = element_text(face = "bold",  size = 8),
      axis.text = element_text(size=6, face="bold"),
         axis.title = element_text(face="bold", size = 10),
         plot.title = element_text(face="bold", size = 10),
         legend.text = element_text(face = "bold",
         size = 6), legend.direction="vertical",
         legend.spacing.y = unit(-0, "cm"),
      legend.title.align=0.5) +
theme(panel.background = element_rect(fill = "white"),
        panel.border = element_rect(colour = "black",
        fill=NA, size=1))+
  scale_color_manual(name = "Taxonomic\ngroup", values = c("#009E73", "#D55E00")) +
  scale_size(name = "Species\ncounts") +
  ylab("Latitude") +
xlab("Longitude") +
guides(color = guide_legend(override.aes = list(size=3)))+
scale_x_continuous(breaks = seq(0, 20, by = 10)) +
scale_y_continuous(breaks = seq(40, 60, by = 10))

```
# Results

>>>>

---
title: "Mapping plant-pollinator interactions across Europe"
latex-tinytex: false
format:
  pdf:
    include-in-header: 
      text: |
        \usepackage{lscape}
        \newcommand{\blandscape}{\begin{landscape}}
        \newcommand{\elandscape}{\end{landscape}}
---

```{r Load libraries, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE}
library(dplyr) #For handling fata 
library(ggplot2) #For plotting
library(giscoR) #For plotting
library(sf) #For handling coordinates and plotting
library(patchwork)#For plotting
library(ggstar) #For plotting (cool shapes)
library(scales) #For plotting (decimals on axes)
```

@@

Pollinators play a crucial role in maintaining Earth's terrestrial biodiversity and human food production by mediating sexual reproduction for most flowering plants. However, their diversity and role as pollinators are increasingly compromised by rapid human-induced environmental changes. One of the major challenges for pollinator conservation, is the lack of robust generalisable data across space and time to comprehend the conservation status and population trends among different pollinator species. Here, we present a dataset of plant-pollinator interactions at European level that consists of `r study_number` studies distributed across `r country_number` countries that comprise over a million of interactions between plants and pollinators. The dataset includes a total of `r pollinator_spp_number` pollinator and `r plant_spp_number` plant species that accounts approximately for 30% of each of the main pollinator groups (i.e., bees, syrphids and butterflies) and 5% of flowering plants that inhabit the European continent.

@@

Shared species across studies (describe trend), added now in graph 1?

Update graph 1 (Add shared species of plants and pollinators?)

@@

To calculate the completeness of the dataset

```{r echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, out.width="110%", fig.cap= "Figure 1"}

#Load data
data = readRDS("../Data/Interactions_uncounted.rds")

#Prepare coordinates
for_plotting = data %>% 
select(Study_id, Latitude, Longitude) %>% 
distinct()
#Get countries and transfrom coordinates
countries <- gisco_get_countries(
resolution = 20) %>%
st_transform(3035) %>% 
sf::st_as_sf(crs = 4326)

#Number of plant and poll species per network
#-----------------------#
#Pollinators------
#-----------------------#
#Check unique number of pollinator species
PollNumber_by_ID = data %>% 
select(Pollinator_rank, Pollinator_accepted_name, Study_id) %>% 
filter(Pollinator_rank == "SPECIES") %>% 
select(Pollinator_accepted_name, Study_id) %>% 
group_by(Study_id) %>% 
summarise(Pollinator_counts = n_distinct(Pollinator_accepted_name))
#Merge now with spp counts by network dataset
poll_data = left_join(PollNumber_by_ID, for_plotting, by = "Study_id")
#Create duplicate cord columns to operate on them
poll_data$coords <- data.frame(
Longitude = poll_data$Longitude, Latitude = poll_data$Latitude)
#Set coordinates
poll_data$coords_sf = st_as_sf(poll_data$coords, 
  coords = c("Longitude", "Latitude"), crs = 4326)
#Plot map of Europe
#Very noisy with many coordinates per point,
#Let's select a unique coordinate by study
poll_data1 =  poll_data %>% 
distinct(Study_id, .keep_all = TRUE)

#-----------------------#
#Plants-----
#-----------------------#
#Check unique number of plant species
PlantNumber_by_ID = data %>% 
select(Plant_rank, Plant_accepted_name, Study_id) %>% 
filter(Plant_rank == "SPECIES") %>% 
select(Plant_accepted_name, Study_id) %>% 
group_by(Study_id) %>% 
summarise(Plant_counts = n_distinct(Plant_accepted_name))
#Merge now with spp counts by network dataset
plant_data = left_join(PlantNumber_by_ID, for_plotting, by = "Study_id")
#Create duplicate cord columns to operate on them
plant_data$coords <- data.frame(
Longitude = plant_data$Longitude, Latitude = plant_data$Latitude)
#Set coordinates
plant_data$coords_sf = st_as_sf(plant_data$coords, 
  coords = c("Longitude", "Latitude"), crs = 4326)
#Plot map of Europe
#Very noisy with many coordinates per point,
#Let's select a unique coordinate by study
plant_data1 =  plant_data %>% 
distinct(Study_id, .keep_all = TRUE)

#Add vars
plant_data1$Group = "Plant"
poll_data1$Group = "Pollinator"
#Rename cols
plant_data2 = plant_data1 %>% 
rename(Counts = Plant_counts)
poll_data2 = poll_data1 %>% 
rename(Counts = Pollinator_counts)
#Bind rows
all_data = bind_rows(plant_data2, poll_data2)

#Try to plot both together (same plot)
map = ggplot(countries) +
geom_sf(fill="floralwhite",color = "black", 
        alpha = 1,linewidth=0.1) + 
geom_star(data = all_data, alpha=1,aes(x= Longitude, y=Latitude,
           size=Counts, starshape = Group, color= Group))+  
coord_sf(crs = st_crs(3035), default_crs = st_crs(4326),
         xlim = c(-14, 39), ylim = c(37, 70))+
theme(panel.grid.major = element_blank(), 
      legend.position = ("top"),
      legend.box = "vertical",
      legend.background = element_blank(),
      legend.box.background = element_blank(),
      legend.key = element_blank(), 
      legend.title = element_text(face ="bold",  size = 6),
      legend.box.spacing = unit(0.2, "cm"),
      legend.margin=margin(0,0,0,0),
        legend.box.margin=margin(-10,-10,-10,-10),
      axis.text = element_text(size=6,                  face="bold"),
      axis.title = element_text(face="bold", size = 8),
         legend.text = element_text(size = 6),                           legend.direction="horizontal",
         legend.spacing.y = unit(-0.3, "cm"),
      legend.title.align=0.5) +
theme(panel.background = element_rect(fill = "aliceblue"),
        panel.border = element_rect(colour = "black",
        fill=NA, size=1)) + 
 scale_size_continuous(name= "Species counts",range = c(0, 3.75))+
scale_color_manual(values=c("#009E73", "#D55E00"),
         guide="none") +
scale_starshape_manual(name = "Taxonomic group",             values = c(15, 7),
             guide=guide_legend(reverse=TRUE,
             override.aes=list(
                 size=2,
                 color=c("Pollinator"= "#D55E00","Plant"="#009E73")))) +
  ylab("Latitude") +
xlab("Longitude") +
scale_x_continuous(breaks = seq(0, 20, by = 10)) +
scale_y_continuous(breaks = seq(40, 60, by = 10)) +
guides(color = "none", size=guide_legend(nrow=1,override.aes = list(starshape =c(15,15, 15), size=c(0.8,1.8,2.8)))) + 
ggtitle("(a)") +
theme(plot.title = element_text(vjust = -12, hjust=0.1, size=10))

#----------------#
#Pollinators
#----------------#
#First select cols of rank, accepted name and study ID
#Then select unique levels by study ID
#Now sum levels (maximum can be as maximum number of studies)
poll_spread = data %>% 
select(Pollinator_rank, Pollinator_accepted_name, Study_id) %>% 
group_by(Study_id) %>% 
filter(Pollinator_rank == "SPECIES") %>% 
distinct(Pollinator_accepted_name) %>% 
ungroup() %>% 
count(Pollinator_accepted_name) %>% 
rename(n_studies_shared = n) %>% 
arrange(-n_studies_shared) %>% 
mutate(Percent_total = n_studies_shared / n_distinct(data$Study_id))

#Seelect quantile 50% from the total number of species
spp_number = poll_spread %>%  
select(Pollinator_accepted_name) %>% 
n_distinct()
df = seq(1, spp_number)
quantile_50 = quantile(df, 0.5)

#Obtain most common pollinator for plotting
most_common_poll = poll_spread %>% filter(n_studies_shared == max(n_studies_shared)) %>%
select(Pollinator_accepted_name) %>% pull()

#Plot
p1 = ggplot(poll_spread, 
aes(reorder(Pollinator_accepted_name,-Percent_total), Percent_total)) +
geom_bar(stat = "identity", 
           color = "#D55E00",
           lwd = 0.015, fill = "#D55E00") +
ylab("Shared pollinators (%)") +
theme_minimal()+
theme(axis.text.x = element_blank(),
  axis.ticks.x=element_blank(),
  axis.ticks.y = element_line(size = 0.2),
  plot.title = element_text(size = 8, face = "bold"), 
  axis.text.y = element_text(size=6),
  panel.grid.major.x = element_blank(),
  panel.grid.minor.y = element_blank(),
  panel.grid.major.y = element_line(size=0.2, linetype =           2)) +
xlab(NULL) +
ylab(NULL) + 
ggtitle("Pollinators")+
geom_vline(xintercept = quantile_50, linetype="dashed", 
color = "black", size=0.25) + 
annotate(geom="text", x=1285, y=0.83, label="50th percentile",          color="black", size = 1.5) +
annotate(geom="text", x=20, y=0.88, label=most_common_poll[1],         color="black",  fontface = 'italic', size = 1.5)+
scale_y_continuous(breaks = seq(0, 0.75, by= 0.25), expand = c(0, 0)) + 
annotate(geom="text", x=-500, y=1.15, label="(b)",color="black", size = 3.5) +
coord_cartesian(xlim=c(0, nlevels(factor(poll_spread$Pollinator_accepted_name))),ylim=c(0, max(poll_spread$Percent_total)), clip="off")

#----------------#
#Plants
#----------------#
plant_spread = data %>% 
select(Plant_rank, Plant_accepted_name, Study_id) %>% 
group_by(Study_id) %>% 
filter(Plant_rank == "SPECIES") %>% 
distinct(Plant_accepted_name) %>% 
ungroup() %>% 
count(Plant_accepted_name) %>% 
rename(n_studies_shared = n) %>% 
arrange(-n_studies_shared) %>% 
mutate(Percent_total = n_studies_shared / n_distinct(data$Study_id))

#Seelect quantile 50% from the total number of species
spp_number = plant_spread %>%  
select(Plant_accepted_name) %>% 
n_distinct()
df = seq(1, spp_number)
quantile_50 = quantile(df, 0.5)

#Obtain most common plant for plotting
most_common_plant = plant_spread %>% filter(n_studies_shared == max(n_studies_shared)) %>%
select(Plant_accepted_name) %>% pull()

#Plot
p2 = ggplot(plant_spread, 
aes(reorder(Plant_accepted_name,-Percent_total), Percent_total, fill = Plant_accepted_name)) +
geom_bar(stat = "identity", 
           color = "#009E73",
           lwd = 0.015, fill = "#009E73") +
ylab("Shared plants (%)") +
theme_minimal()+
theme(axis.text.x = element_blank(),
         axis.ticks.x=element_blank(),
         axis.ticks.y = element_line(size = 0.2),
         axis.title.x = element_text(face = "bold", size = 8),            plot.title = element_text(size = 8, face = "bold"),
         axis.text.y = element_text(size=6),
         panel.grid.major.x = element_blank(),
         panel.grid.minor.y = element_blank(),
         panel.grid.major.y = element_line(size=0.2, linetype =           2)) +
xlab("Species") +
ylab(NULL) + 
ggtitle("Plants") + 
geom_vline(xintercept = quantile_50, linetype="dashed", 
          color = "black", size=0.25) + 
annotate(geom="text", x=835, y=0.7, label="50th percentile",color="black", size = 1.5) + 
annotate(geom="text", x=20, y=0.75, label=most_common_plant[1]
      ,color="black",  fontface = 'italic', size = 1.5)+
annotate(geom="text", x=20, y=-0.08, label="Common spp."
      ,color="black",  size = 1.5) +
annotate(geom="text", x=1200, y=-0.08, label="\'Rare\' spp."
      ,color="black",  size = 1.5) + 
scale_y_continuous(breaks = seq(0, 0.6, by= 0.2), expand = c(0, 0), labels = label_number(accuracy = 0.01)) +
coord_cartesian(xlim=c(0, nlevels(factor(plant_spread$Plant_accepted_name))),ylim=c(0, max(plant_spread$Percent_total)), clip="off")

#Prepare panel with plots
plot2 =  wrap_elements(p1 / p2) +  labs(tag ="Occurrence across studies (%)") + 
theme(plot.tag = element_text(size = 7, angle = 90, face = "bold", vjust = -3.5), plot.tag.position = "left")
#Plot everything
map + plot_spacer() + plot2 + plot_layout(widths = c(2.1, -0.45, 1))

# Results
